Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-10-22 paper/paper.qmd
added pollster overview and evaluation

# Appendix {.unnumbered}

>>>>

# Appendix {-}

# Additional Data Details

# Additional Model Details

# Polling Methodology Overview and Evaluation for Siena/NYT

The poll was conducted from Sept. 29 to Oct. 6 and surveyed 3,385 likely voters nationwide and found that Harris led Trump by 49 percent to 46 percent, a slight lead that is within the poll’s margin of error (2.4 points). According to [@nyt-crosstabs], the national poll includes separate polls of 622 voters in Florida, and 617 voters in Texas. The weight given to each of these groups in the national poll has been adjusted so that the overall results are reflective of the entire country. Polls were also conducted by telephone, using live interviewers, in both English and Spanish, with about 98% of respondents were contacted on a cellphone [@nyt-topline]. For battleground polls, voters were called from Arizona, Georgia, Michigan, Nevada, Pennsylvania and Wisconsin [@nyt-methodology] — swing states that have a significant share in electoral college votes). In light of this, responses were also weighted to consider over- and under-represented voters to ensure that each demographic is adequately represented.

This poll employs a random sampling approach of registered voters using telephone interviews, with a focus on both landlines and cellphones. As such, this generally allowed for a representative sample. In addition, NYT/Siena also used voter registration files help ensure proper balance between political parties, and telephone polls have historically proven to be effective in gauging public opinion from recent elections. However, one particular drawback is that telephone response rates are extremely low; in fact, for this poll, “fewer than 2% of contacted individuals participate in the survey.”

In handling non-responses within their questionnaire, for some questions another “sub-question” related to the original is asked only once in order to get a definitive answer; this usually occurs in questions related to leaning (not outright) candidate support. By doing this, it allows NYT to more accurately gauge the public’s opinions. However, at times, they leave non-responses as “Refused” or “Don’t know” often on questions targeted to the individual person (e.g. How has ___ affected you personally?). At this point, there is little no use prodding further in case of a non-response. The overall questionnaire is of high quality (NYT/Siena is one of the most reputable polls after all), and it has its strong and weak points. First, most questions, often those on respondent identification or demographic, are unbiased and fair; in particular, questions on candidate preferences did not contain words suggestive of one candidate over another. However, some questions contain gender-coded language that may skew respondents’ answers in favor of one candidate (e.g. In the question “cares more about people like you” the word “cares” is more often associated with females and so respondents are more likely to choose Harris as the answer, which was seen in the poll results with Harris receiving 49% of responses versus Trump’s 41%).

# Idealized Methodology

## Sampling Approach

## Data Validation
